%\documentclass[sigconf]{acmart}
\documentclass[nonacm,sigconf]{acmart}

\usepackage{paralist}

% Suppress the front-matter blocks that ship with the acmart template.
% The artifact appendix is meant to be appended to the main paper,
% so it carries no title page, authors, or abstract of its own.
\settopmatter{printacmref=false, printccs=false, printfolios=false}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Artifact Appendix for ACM CCS 2026 Paper #1938.
% Two-page limit.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Artifact Appendix}

\textsc{Coin} is an LLM-based Modular Unsafe Function (MUF) detector and
Proof-of-Concept generator for Rust. This artifact provides the
fine-tuned models, evaluation scripts, and convenience launchers needed
to reproduce the main results of the paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Repository}

\textbf{GitHub:} \url{https://github.com/CXWorks/coin-ae}

\noindent\textbf{Zenodo (archived):} \url{https://doi.org/10.5281/zenodo.20709620}

\noindent\textbf{Anonymous mirror:} \url{https://anonymous.4open.science/r/coin-ae-E308}

\noindent Clone with:
\begin{verbatim}
git clone https://github.com/CXWorks/coin-ae.git
cd coin-ae && bash model/reassemble.sh
\end{verbatim}

The repository contains
\texttt{model/} (LoRA adapters, split into \(\leq\)50\,MB parts for GitHub
compatibility),
\texttt{code/} (evaluation and inference scripts),
\texttt{scripts/} (numbered launchers for each experiment),
\texttt{data/} (a reassemblable sample test split and a starter few-shot
file), \texttt{prompts/} (training/inference prompt templates), and
\texttt{custom\_rustc\_patch/} (the \texttt{rustc 1.83.0-dev} patch used
to extract safe-candidate functions).
The full benchmark datasets (\texttt{coin\_test.pkl} --- 319,652 labeled
functions, \texttt{poc\_test.jsonl}, and \texttt{poc\_train\_v2.jsonl})
are submitted separately through the AE system due to size limits.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{System Requirements}

\textbf{Operating system:} Linux x86\_64 (tested on Ubuntu~22.04).

\noindent\textbf{GPU:} A single NVIDIA GPU with $\geq$24\,GB VRAM is
sufficient for the smoke test (E1), PoC evaluation (E3), and the
single-GPU full evaluation; CUDA Compute Capability $\geq$\,8.0
(Ampere or newer) is recommended because \texttt{bitsandbytes} 4-bit
quantization paths target that ISA.
The fast 4-GPU sharded full evaluation (E2) needs four A100-class
80\,GB GPUs; optional PoC re-training (E3) needs $\geq$48\,GB VRAM.
All reported numbers were measured on NVIDIA A100-80\,GB.

\noindent\textbf{CPU / RAM:} 8 CPU cores and 32\,GB RAM minimum
(64\,GB recommended).

\noindent\textbf{Disk:} 20\,GB minimum (50\,GB recommended) for the
conda environment, base model cache, reassembled adapters, and
intermediate evaluation outputs.

\noindent\textbf{Network:} required during setup for HuggingFace
model downloads and (optionally) E4 API calls; not required during
the offline classifier and PoC experiments.

\noindent\textbf{Rust toolchain (optional, E3):} stable + nightly with
Miri, installed via \texttt{rustup}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Package Versions}

The following pinned versions are installed automatically by
\texttt{scripts/0\_setup\_env.sh}:

\medskip
\begin{tabular}{ll}
\texttt{python}        & 3.11 \\
\texttt{torch}         & 2.x (CUDA 12.1 build) \\
\texttt{unsloth}       & \textbf{2025.2.15 (exact)} \\
\texttt{transformers}  & \textbf{4.49.0 (exact)} \\
\texttt{peft}          & 0.14.0 \\
\texttt{trl}           & 0.15.2 \\
\texttt{tokenizers}    & 0.21.0 \\
\texttt{bitsandbytes}  & $\geq$0.43 \\
\texttt{scikit-learn}  & latest \\
\texttt{numpy, matplotlib, tqdm, rich} & latest \\
\texttt{openai}        & $\geq$1.30 (E4 only) \\
\texttt{anthropic}     & $\geq$0.30 (E4 only) \\
\end{tabular}

\medskip
\textbf{Critical:} \texttt{unsloth==2025.2.15} and \texttt{transformers==4.49.0}
must be used \emph{exactly}.
Newer unsloth versions default to a shorter \texttt{max\_seq\_length} when
the argument is omitted, silently truncating long Rust code snippets and
dropping classifier AUPRC from $\approx$0.76 to $\approx$0.32. Do not
upgrade these two pins.
\texttt{eval\_repro.py} relies on this behavior to read
\texttt{max\_seq\_length\,=\,8192} from the checkpoint config.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Security, Privacy, and Ethical Concerns}

Evaluation scripts run read-only inference on the provided datasets.
The PoC evaluation optionally invokes \texttt{cargo build} and
\texttt{cargo +nightly miri run} on generated Rust code inside isolated
\texttt{tempfile} directories; each invocation is short-lived and
self-contained. No persistent file modification or elevated privileges
are required. The PoCs are designed to trigger \emph{detected}
undefined behavior under Miri, not to exploit any external system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Set Up}

\subsubsection{Installation}

\begin{compactenum}
\item Clone the repository (see \emph{Repository} above) and reassemble
      split model files:\\
      \texttt{bash model/reassemble.sh}
\item Create the conda environment and install pinned dependencies:\\
      \texttt{bash scripts/0\_setup\_env.sh}
\item Place \texttt{coin\_test.pkl} and \texttt{poc\_test.jsonl} at
      local paths.
\end{compactenum}

\subsubsection{Basic test}

Verify model load and CUDA access in $\approx$2 minutes with a
500-sample run:
\begin{verbatim}
CUDA_VISIBLE_DEVICES=0 \
./env/bin/python code/eval_repro.py \
  --checkpoint model/llama3.2 \
  --data /path/to/coin_test.pkl \
  --n 500 --output /tmp/smoke.json
\end{verbatim}
Expected: a non-zero AUPRC printed and \texttt{/tmp/smoke.json} created.
If \texttt{ImportError: bitsandbytes} appears, the launcher scripts set
\texttt{LD\_LIBRARY\_PATH} correctly --- prefer those.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Evaluation Workflow}

\subsubsection{Major claims}

\begin{compactitem}
\item[(C1):]
  \textsc{Coin}'s fine-tuned Llama~3.2-3B classifier achieves
  AUPRC\,=\,0.82 on the MUF detection task, and 63.7\% precision
  with 80.4\% recall after PAC-based threshold calibration ---
  substantially outperforming the vanilla Llama~3.2-3B (AUPRC\,=\,0.021),
  QWen3-4B (0.030), GPT-4o, and Claude-3.7.
  Proven by experiments (E1) and (E2); results reported in
  Figure~2 and Table~2 of the paper.

\item[(C2):]
  \textsc{Coin}'s fine-tuned PoC generator produces compilable,
  root-cause-demonstrating PoC code for 19 out of 22 in-the-wild
  MUF bugs found in the crates.io evaluation; the generated PoCs
  were submitted to developers and contributed to 14 confirmed bugs
  and 10 CVE assignments.
  Proven by experiment (E3); results reported in Table~4.

\item[(C3):]
  \textsc{Coin} substantially outperforms vanilla open-source LLMs
  (Llama~3.2 3B, Llama~3.1 8B, Qwen3 4B; AUPRC\,$\approx$\,0.02--0.03)
  and closed-source GPT-4o / Claude-3.7 even with few-shot context
  and Best-of-K querying (precision on the unsafe class never exceeds
  $\approx$7\%).
  Proven by experiment (E4); results reported in Figure~2 and Tables~2--3.
\end{compactitem}

\subsubsection{Experiments}

\begin{compactitem}
\item[(E1):]
  \textbf{Classifier smoke test}
  [5 person-minutes + 20 compute-minutes + 10\,GB disk]:
  Verify the fine-tuned Llama~3.2-3B classifier achieves
  AUPRC\,$\approx$\,0.75 on a stratified 8,000-example sample,
  supporting (C1).

  \begin{asparadesc}
  \item[Preparation:] Complete Setup steps; confirm
        \texttt{unsloth.\_\_version\_\_ == "2025.2.15"}.
  \item[Execution:]
\begin{verbatim}
bash scripts/1_smoke_test.sh \
  /path/to/coin_test.pkl
\end{verbatim}
  \item[Results:] The script prints AUPRC, precision, recall, F1 and
        saves them to \texttt{/tmp/eval\_smoke.json}.
        Expected: AUPRC\,$\approx$\,0.7529,
        recall(unsafe)\,$\approx$\,0.805.
        If AUPRC\,$\approx$\,0.30--0.35, the unsloth version is wrong.
  \end{asparadesc}

\item[(E2):]
  \textbf{Full classifier evaluation}
  [10 person-minutes + 2.5 compute-hours (4-GPU) or 10 compute-hours
  (1-GPU) + 10\,GB disk]:
  Reproduce the AUPRC on the complete 319,652-sample test set,
  supporting (C1).

  \begin{asparadesc}
  \item[Preparation:] Same as E1. The 4-GPU option requires four
        A100-class GPUs (one shard each).
  \item[Execution:]
\begin{verbatim}
# 4-GPU (~2.5 h)
bash scripts/2_full_eval.sh \
  /path/to/coin_test.pkl
# Single-GPU (~10 h)
NUM_SHARDS=1 \
  bash scripts/2_full_eval.sh \
  /path/to/coin_test.pkl
\end{verbatim}
  \item[Results:] Aggregate AUPRC and precision-at-recall-0.8 are
        printed and saved to \texttt{/tmp/eval\_full\_merged.json}.
        Expected: AUPRC\,$\approx$\,0.764 on the fixed stratified split.
        The paper's AUPRC\,=\,0.82 is measured on the natural class
        distribution of the full crate corpus; the $\approx$0.06 gap
        reflects this ratio difference (see ARTIFACT\_EVALUATION.md).
  \end{asparadesc}

\item[(E3):]
  \textbf{PoC generator evaluation}
  [10 person-minutes + 1 compute-hour + 5\,GB disk]:
  Evaluate the fine-tuned PoC generator on held-out MUF examples,
  measuring safe-caller compliance, compilation rate, and
  Miri-detected UB rate, supporting (C2).

  \begin{asparadesc}
  \item[Preparation:] Place \texttt{poc\_test.jsonl} at a local path.
        For \texttt{compiles}/\texttt{ub\_detected}, install Rust and
        nightly Miri (\texttt{rustup component add miri --toolchain nightly}).
        Miri is optional; without it, only \texttt{safe\_caller} is
        meaningful.
  \item[Execution:]
\begin{verbatim}
bash scripts/3_poc_eval.sh \
  /path/to/poc_test.jsonl
\end{verbatim}
        To reproduce fine-tuning from scratch ($\approx$3 h on one A100):
\begin{verbatim}
TRAIN=1 \
TRAIN_DATA=/path/to/poc_train_v2.jsonl \
bash scripts/3_poc_eval.sh \
  /path/to/poc_test.jsonl
\end{verbatim}
  \item[Results:] The script reports per-example and aggregate
        \texttt{safe\_caller} (no \texttt{unsafe} in \texttt{fn main()}),
        \texttt{compiles} (\texttt{cargo build} passes), and
        \texttt{ub\_detected} (\texttt{miri} flags UB), saved to
        \texttt{/tmp/poc\_eval.json}. The fine-tuned model generates
        valid PoC skeletons for the majority of test examples,
        consistent with the 19/22 success rate in Table~4.
  \end{asparadesc}

\item[(E4):]
  \textbf{Baseline comparison}
  [15 person-minutes + 2 compute-hours + a few US\$ in API credits + 30\,GB
  disk]: Reproduce the comparison against vanilla open-source LLMs
  (paper Fig.~2) and closed-source GPT-4o / Claude-3.7 (paper
  Tables~2--3), supporting (C3).

  \begin{asparadesc}
  \item[Preparation:] Export the API keys you have available
        (\texttt{OPENAI\_API\_KEY}, \texttt{ANTHROPIC\_API\_KEY}); the
        launcher skips a provider whose key is missing. Llama models
        on HuggingFace are gated --- set \texttt{HF\_TOKEN} or run
        \texttt{huggingface-cli login} once. The provided
        \texttt{data/shots.jsonl} contains five labeled examples for
        zero-friction few-shot runs; larger shot files follow the
        format documented at the top of \texttt{eval\_api\_baseline.py}.
  \item[Execution:]
\begin{verbatim}
bash scripts/4_baseline_eval.sh \
  /path/to/coin_test.pkl
\end{verbatim}
        Or one configuration directly:
\begin{verbatim}
# Open-source: Llama 3.2 3B vanilla
./env/bin/python \
  code/eval_open_baseline.py \
  --model meta-llama/Llama-3.2-3B-Instruct \
  --data /path/to/coin_test.pkl \
  --n 8000 --output /tmp/open_llama32.json
# API: GPT-4o, N=3 few-shot, Best@1
./env/bin/python \
  code/eval_api_baseline.py \
  --provider openai --model gpt-4o \
  --data /path/to/coin_test.pkl --n 200 \
  --shots_file data/shots.jsonl --shots_n 3 \
  --best_of 1 --output /tmp/gpt4o_n3.json
\end{verbatim}
        The launcher iterates N\,$\in\,\{0,1,3,5\}$ (Table~2) and N=1
        with K\,$\in\,\{3,5\}$ (Table~3) for each provider.
  \item[Results:] Per-config JSON files in \texttt{/tmp/coin\_baselines/}.
        Expected: vanilla open-source AUPRC $\approx$ 0.02--0.03
        (Fig.~2); GPT-4o precision/recall on the unsafe class
        $\approx$\,4--5\,\% / 21\,\%; Claude-3.7 precision/recall
        $\approx$\,4--7\,\% / 7--12\,\%, matching the order of
        magnitude in Tables~2--3. Coin's reproduced
        precision/recall = 63.7\,\% / 80.4\,\% (E2) is one to two
        orders of magnitude better.
  \end{asparadesc}

\end{compactitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Notes on Reusability}

\texttt{code/infer\_batch.py} runs the classifier on any Rust crate
directory and outputs a per-function CSV of MUF probabilities, enabling
application to new codebases. \texttt{code/threshold.py} provides
PAC-based threshold calibration for specific
precision/recall operating points. \texttt{code/gen\_poc.py --infer}
accepts arbitrary MUF function text and category labels, allowing the
PoC generator to be applied to MUFs found by other tools. Both adapters
load via standard PEFT/HuggingFace APIs independently of the included
scripts, facilitating integration into custom workflows.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Version}
Based on the LaTeX template for Artifact Evaluation V20220926.

\end{document}
\endinput
